%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15) 
%
% This template has been downloaded from:
% https://github.com/mlda065/friggeri-letter
%
% Original author: 
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Modifications by Matthew Davis (matthew@mdavis.xyz)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
% Important notes:
% This template needs to be compiled with XeLaTeX 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
 

\begin{document} 
 
\header{Samuel}{Pilla}{Software Developer} % Your name and current job title/field 

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION 
%----------------------------------------------------------------------------------------


\aside{contact}{
%don't display the name in the contact details on the first page
%because it's up the top
%That's why there's the if statement
\ifx \firstPage \undefined
   \xdef\firstPage{}
\else
Samuel Pilla \\
~ \\
\fi
4055 Laclede Avenue \\
St. Louis, MO 63108 \\
~  \\
(314) 225-5470 \\
~   \\
\href{mailto:samuelpilla13@gmail.com}{samuelpilla13@gmail.com} \\
\href{github.com/ArthurSemilla}{github.com/ArthurSemilla} \\
}
 




%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
 
\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry 
{2016--Now}
{AT\&T}
{St. Louis, MO}%side thing
{Associate Applications Developer}
{
Developer on the AT\&T Integrated Cloud as an upstream developer for the OpenStack project, an open source cloud software suite. Primarily coded in Python and focused on security aspects of the project, specifically Keystone, the authentication service.
}

\entry 
{2015--2015}
{Boeing}
{Huntington Beach, CA}%side thing
{Network Engineer Intern}
{
Maintained the multiple site's network inrastructure through the configuration of network devices, design and planning for building wired and wireless networks, and the security of all networking systems.
}

%------------------------------------------------

\end{entrylist}

\subsection{Part Time}

\begin{entrylist}


\entry
{2012--2015}
{Missouri S\&T IT}
{Rolla, MO}
{Desktop Engineer}
{ 
Ensured sotware applications were packaged and deployed to campus machines and maintain the proper functionality and permissions for the applications.
}

\entry
{2015--2016}
{Missouri S\&T}
{Rolla, MO}
{Teacher's Assistant}
{ 
Assisted in the Introduction to Computer Science lab by teaching students proper coding techniques for C++. Also graded the work of students in the lecture that is paired with the mentioned lab.
}

%------------------------------------------------


\end{entrylist}


%------------------------------------------------


\subsection{Community Roles}

\begin{entrylist}


\entry
{2012-Now}
{Organisation name} 
{}
{Role}
{
description
}


%------------------------------------------------


\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\section{education}

\begin{entrylist} 

%------------------------------------------------

\entry
{2012--2016}
{Bachelor {\normalfont of Computer Science}}
{University of Missouri S\&T}
{GPA 3.16}
{
Focused on object oriented programming, data mathematics in coding, and well rounded non-computer learning. Electives: Object Oriented Numerical Modelling, Data Mining, Artificial Intelligence, Abnormal Psychology
}

%------------------------------------------------

\entry
{2008--2012}  
{High School Certificate}
{St. Louis University High School}
{GPA 3.20} 
{
}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2012}
{Bright Flight Scholarship}
{Missouri, USA} 
{} 
{Awarded for achieving a 31 or higher on the ACT.}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%	Technical SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{technical skills}

\begin{entrylist}

%------------------------------------------------



\entry
{}
{Software}
{}
{}
{
Git, Unix/Linux, Microsoft Office, Visual Studio, Configuration Manager
}

%------------------------------------------------


\entry
{}
{Programming}
{}
{}
{
Confident with Python, C++ \LaTeX, Ruby, Perl, C\#
}

%------------------------------------------------



\end{entrylist}



%----------------------------------------------------------------------------------------
%	Human SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{human skills}

\begin{entrylist}

%------------------------------------------------



\entry
{}
{Leadership}
{}
{}
{

}

%------------------------------------------------


\entry
{}
{Teamwork}
{}
{}
{
Worked across layers of teams, from small internal teams to large worldwide open source teams.
}

%------------------------------------------------



\end{entrylist}


%----------------------------------------------------------------------------------------
%	References SECTION 
%----------------------------------------------------------------------------------------

\section{references}


\begin{entrylist}


\entry
{}
{Name}
{Company/Organisation}
{Title}
{
Contact details here
}


\entry
{}
{Name}
{Company/Organisation}
{Title}
{
Contact details here
}

\end{entrylist} 

%----------------------------------------------------------------------------------------

\end{document}